Viscous Transport in Eroding Porous Media

### 2019-08-08 docs/transport/erosion_transport.tex
small changes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{50 nearly touching bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\color{red}
The second nearly touching bodies case is 50 bodies in a Hagen-Poiseuille flow.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{100 bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
 \begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =0.9\linewidth]{./figs/100b_50}
\caption{100 bodies and porosity = 55.54\% at t= 0.005}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =1.1\linewidth]{./figs/100b_100}
\caption{99 bodies and porosity = 62.98\% at t= 0.01}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =0.9\linewidth]{./figs/100b_150}
\caption{94 bodies and porosity = 72.22\% at t= 0.015}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =1.1\linewidth]{./figs/100b_200}
\caption{82 bodies and porosity = 83.37\% at t= 0.02}
\end{subfigure}
\caption{\label{fig:Eroding100vort} Erosion of 100 bodies with the
  fixed-pressure-drop condition. The color is the vorticity of fluid. In
  this simulation, we use $N_\iin = 256$ discretization points on the
  body, $N_\out = 1024$ points on the outer wall, a time-step of
  $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and
  $\sigma=10/256$.}
\end{figure}

@@

To measure the local behavior of fluid quantitatively, 
we use the velocities and local tortuosities at the starting cross section 
to analysis the interaction of fluid and bodies until the end cross section 
in Fig.~\ref{fig:Eroding100tort}(b) and (c).
In Fig.~\ref{fig:Eroding100tort}(b) the graph represents the ratio of the
x-component velocity u(-1, y) to its maximum velocity $u_{max}=3.9021
\times 10^{-4}$ at equal spreading tracers on the strating cross section.
As in the case of 20 nearly touching bodies, the velocity is continuous along
the starting cross section and acting as a Poiseuille flow in the channel between
bodies. When the fluid is close to bodies
the speed of fluid will be slow down because of the no-slip condition on the bodies
and this causes the separated branches of the inlet flow.
The maximum velocity of the fluid with 100 bodies on the starting cross 
section is slower than the maximum velocity of the fluid with 20 bodies
but the velocity in the case of 100 bodies 
changes more rapidly than the velocity of the fluid with 20 bodies.
The reason of the rapid change on the starting cross section of 
100-body case is because there are 
more bodies near the starting cross section in
100-body case than in the 20-body case. 
so the inlet flow in 100-body case
will be separated into more branches than the flow in 20-body case.

In Fig.~\ref{fig:Eroding100tort}(c) we record the 
local tortuosity $\tau(y)$ for $y$ on the starting cross section x = -1.
It is a discontinous function and the maximum of $\tau$ in the case of 100 bodies
is 1.2547 and the minimum is 1.0003. This function $\tau$
has more jumps than the one in the case of 20 bodies but its maximum 
is smaller than the maximum in the case of 20 bodies. 
The jump in this graph means the neighboring trajectories are splitted by bodies
so it is reasonable to have more jumps in the case of 100-body than the case of 20-body
since there are more bodies in the former case.

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[width = \textwidth]{./figs/100b_t100tracer}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.45\textwidth}
\begin{subfigure}[b]{\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc100}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local100}
\caption{}
\end{subfigure}
\end{subfigure}

\caption{\label{fig:Eroding100tort} The tortuosity study in the fluid with 100 bodies 
when the porosity is 62.98 \%.
(a) The historical trajectories of 
200 tracers released at x = -1 in the fluid with multiple bodies.
(b) The 
x-component velocity u(-1, y) with respect to its maximum velocity $u_{max}=3.9021
\times 10^{-4}$ at equal spreading tracers on the cross section x = -1. 
(c) The local tortuosity $\tau(y)$ on the cross section x = -1. 
}
%(c) The difference of $\tau(y)$ at two neighboring tracers on the cross section x = -1.
%(d) The ratio of the minimum to maximum speeds along the trajectories of tracers.}
\end{figure}

@@

\begin{figure}[H]
\center
\includegraphics*[width =0.45\linewidth]{./figs/100b_first_moment}
\includegraphics*[width =0.45\linewidth]{./figs/100b_second_moment}
\caption{\label{fig:Eroding100anomalous} The analysis of anomalous diffusion in
 100 bodies with respect to five porosities and the reference line of 100\% porosity.
The first moment (left) is the mean length of streamlines and the second moment (right) is the }
\end{figure}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{50 eroding bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\color{red}
The second nearly touching bodies case is 50 bodies in a Hagen-Poiseuille flow.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{100 eroding bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
As a final example, we consider 100 eroding bodies with an initial
porosity near 55\%.  Snapshots of the configurations and vorticity are
in Figure~\ref{fig:Eroding100vort}.

\begin{figure}[H]
 \begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =0.9\linewidth]{./figs/100b_50}
\caption{100 bodies and porosity = 55.54\% at t= 0.005}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =1.1\linewidth]{./figs/100b_100}
\caption{99 bodies and porosity = 62.98\% at t= 0.01}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =0.9\linewidth]{./figs/100b_150}
\caption{94 bodies and porosity = 72.22\% at t= 0.015}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =1.1\linewidth]{./figs/100b_200}
\caption{82 bodies and porosity = 83.37\% at t= 0.02}
\end{subfigure}
\caption{\label{fig:Eroding100vort} Erosion of 100 bodies with the
  fixed-pressure-drop condition. The color is the vorticity of fluid. In
  this simulation, we use $N_\iin = 256$ discretization points on the
  body, $N_\out = 1024$ points on the outer wall, a time-step of
  $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and
  $\sigma=10/256$.}
\end{figure}

To quantify the tortuosity, we compute the relative velocity
(Figure~\ref{fig:Eroding100tort}(a)) and the local tortuosity
(Figure~\ref{fig:Eroding100tort}(b)) of 1000 tracers placed immediately
to the left of the porous region at $x=-1$.  The porosity at this
instance in time is $62.98\%$ and the maximum velocity at $x=-1$ is
$3.90 \times 10^{-4}$. The initial velocity of the tracers is
qualitatively similar to the 20 body example
(Figure~\ref{fig:Eroding20tort}(a)), except with additional maximum and
minimums because of the additional bodies.  Compared to
Figure~\ref{fig:Eroding20tort}(b), the local tortuosity is much more
discontinuous.  These discontinuities can be explained by examining the
trajectories of tracers in Figure~\ref{fig:Eroding100tort}(c).  Here,
there are many instances of neighboring trajectories that are deflected
apart from one another as they tend to a stagnation point in the flow,
and this results in trajectories with significantly different lengths.
At this instance in time one the tracers travels 25.5\% farther than it
would have if the bodies had been absent, and the average tracer
travelled ???\% farther than it would have if the bodies were absent.
Therefore, at this instance in time, the tortuosity is $1.???$
\todo[inline]{S-H: Fill in the numbers in this paragraph}

\begin{figure}[H]
\begin{subfigure}[b]{0.45\textwidth}
\begin{subfigure}[b]{\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc100}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local100}
\caption{}
\end{subfigure}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[width = \textwidth]{./figs/100b_t100tracer}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding100tort} The tortuosity study in the fluid
with 100 bodies when the porosity is 62.98\%.  (a) The x-component
velocity u(-1, y) with respect to its maximum velocity $u_{max}=3.9021
\times 10^{-4}$ at equal spreading tracers on the cross section x = -1.
(b) The local tortuosity $\tau(y)$ on the cross section x = -1. (c) The
trajectories of 200 tracers released at $x = -1$ in the fluid with
multiple bodies.}
\end{figure}

@@

@@

@@

\begin{figure}[H]
\center
\includegraphics*[width =0.45\linewidth]{./figs/100b_first_moment}
\includegraphics*[width =0.45\linewidth]{./figs/100b_second_moment}
\caption{\label{fig:Eroding100anomalous} The analysis of anomalous
diffusion in 100 bodies with respect to five porosities and the
reference line of 100\% porosity.  The first moment (left) is the mean
length of streamlines and the second moment (right) is the 
\todo[inline]{Slope of the top black line is 0.8715}
}
\end{figure}

@@

%To measure the local behavior of fluid quantitatively, 
%we use the velocities and local tortuosities at the starting cross section 
%to analysis the interaction of fluid and bodies until the end cross section 
%in Fig.~\ref{fig:Eroding100tort}(b) and (c).
%In Fig.~\ref{fig:Eroding100tort}(b) the graph represents the ratio of the
%x-component velocity u(-1, y) to its maximum velocity $u_{max}=3.9021
%\times 10^{-4}$ at equal spreading tracers on the strating cross section.
%As in the case of 20 nearly touching bodies, the velocity is continuous along
%the starting cross section and acting as a Poiseuille flow in the channel between
%bodies. When the fluid is close to bodies
%the speed of fluid will be slow down because of the no-slip condition on the bodies
%and this causes the separated branches of the inlet flow.
%The maximum velocity of the fluid with 100 bodies on the starting cross 
%section is slower than the maximum velocity of the fluid with 20 bodies
%but the velocity in the case of 100 bodies 
%changes more rapidly than the velocity of the fluid with 20 bodies.
%The reason of the rapid change on the starting cross section of 
%100-body case is because there are 
%more bodies near the starting cross section in
%100-body case than in the 20-body case. 
%so the inlet flow in 100-body case
%will be separated into more branches than the flow in 20-body case. 
%
%In Fig.~\ref{fig:Eroding100tort}(c) we record the 
%local tortuosity $\tau(y)$ for $y$ on the starting cross section x = -1.
%It is a discontinous function and the maximum of $\tau$ in the case of 100 bodies
%is 1.2547 and the minimum is 1.0003. This function $\tau$
%has more jumps than the one in the case of 20 bodies but its maximum 
%is smaller than the maximum in the case of 20 bodies. 
%The jump in this graph means the neighboring trajectories are splitted by bodies
%so it is reasonable to have more jumps in the case of 100-body than the case of 20-body
%since there are more bodies in the former case.
